RED WINE DATA by Paula Hwang 
========================================================

This report explores a dataset containing quality and attributes for approximately 1600 wines.

```{r echo=FALSE, message=FALSE, warning=FALSE, packages}
getwd()
setwd('C:\\Users\\Alexander Smith\\Desktop\\wine-data')

df <- read.csv('C:\\Users\\Alexander Smith\\Desktop\\Red_Wine\\wineQualityReds.csv')

library(ggplot2)
```

Our dataset consists of 13 variables, with almost 1599 observations.

####Display variables and observations
```{r echo=FALSE, Load_the_Data}
# Load the Data
dim(df)
```

####Display the summary of the data
```{r echo=FALSE, Load_the_summary1}
# Load the Data
str(df)
```

####Display a summary another way
```{r echo=FALSE, Load_the_summary2}
summary(df)
```

# Univariate Plots Section

> **Tip**: In this section, you should perform some preliminary exploration of
your dataset. Run some summaries of the data and create univariate plots to
understand the structure of the individual variables in your dataset. Don't
forget to add a comment after each plot or closely-related group of plots!
There should be multiple code chunks and text sections; the first one below is
just to help you get started.

```{r echo=FALSE, Univariate_Plots}

```

> **Tip**: Make sure that you leave a blank line between the start / end of
each code block and the end / start of your Markdown text so that it is
formatted nicely in the knitted text. Note as well that text on consecutive
lines is treated as a single space. Make sure you have a blank line between
your paragraphs so that they too are formatted for easy readability.

# Univariate Analysis

***A** First, I made a plot to find out what it looks like as a plot.
I decided to pick quality for the univariate Analysis.

source: https://stackoverflow.com/questions/38788357/change-bar-plot-colour-in-geom-bar-with-ggplot2-in-r

####Plot a histogram 
```{r echo=FALSE, Univariate - skewed plot}
qplot(x = quality, data = df, binwidth = 1, colour=I("black"), fill = I("lightblue")) +
    scale_x_continuous(breaks = seq(0,10,1), limits = c(0,10))

```

Because my plot looks slightly skewed, I plan to transform it into a normal distribution. I have two options: sqrt or log.

*source: https://stats.stackexchange.com/questions/74537/log-or-square-root-transformation-for-arima

***B)** This is my attempt of using sqrt to transform into a normal distribution. It looks slightly normal.

####Plot the histogram by adding scale_y_sqrt()
```{r Univariate-sqrt-normal-distribution, echo=FALSE}
qplot(x = quality, data = df, binwidth = 1,colour=I("black"), fill = I("lightblue")) +
    scale_x_continuous(breaks = seq(0,10,1), limits = c(0,10))+
    scale_y_sqrt()
```

***C** This is my attempt of using log10 to transform into a normal distribution. It looks like a perfect normal distribution.

####Plot a histogram with log10
```{r echo=FALSE,message=FALSE, warning=FALSE, Univariate-log10-normal-distribution }
qplot(x = quality, data = df, binwidth = 1, colour=I("black"), fill = I("lightblue")) +
    scale_x_continuous(breaks = seq(0,10,1), limits = c(0,10))+
    scale_y_log10()
```

### What is the structure of your dataset?

- Our dataset consists of 13 variables, with almost 1599 observations.

For more information, read [Cortez et al., 2009].

   Input variables (based on physicochemical tests):
   1 - fixed acidity (tartaric acid - g / dm^3)
   2 - volatile acidity (acetic acid - g / dm^3)
   3 - citric acid (g / dm^3)
   4 - residual sugar (g / dm^3)
   5 - chlorides (sodium chloride - g / dm^3
   6 - free sulfur dioxide (mg / dm^3)
   7 - total sulfur dioxide (mg / dm^3)
   8 - density (g / cm^3)
   9 - pH
   10 - sulphates (potassium sulphate - g / dm3)
   11 - alcohol (% by volume)
   Output variable (based on sensory data): 
   12 - quality (score between 0 and 10)

####Diaplay the dimmensions of an Object like in the begining
```{r echo=FALSE, dataset}
dim(df)
```

### What is/are the main feature(s) of interest in your dataset?

- My main feature of interest is the quality of the wine. 

### What other features in the dataset do you think will help support your \
investigation into your feature(s) of interest?

- I believe that that I am interesting in all the variables such as volatile.acidity, residual.sugar, free.sulfur.dioxide, density, sulphates, fixed acidity, citric-acid, chlorides, pH, and alcohol. 

```{r message = FALSE, warning = FALSE, echo = FALSE, fig.width=20, fig.height=20, grid part 1}

library(grid)
library(gridExtra)

p1 <- qplot(x = volatile.acidity,data = df) 

p2 <- qplot(x = residual.sugar,data = df)

p3 <- qplot(x = free.sulfur.dioxide, data = df)
  scale_x_continuous(breaks = seq(0, 50, 5))

p4 <- qplot(x = density, data = df) +
  scale_y_continuous(breaks = seq(0, 200, 30))

p5 <- qplot(x = sulphates, data = df)

p6 <-qplot(x = fixed.acidity, data = df)

p7 <- qplot(x = citric.acid, data = df)

p8 <- qplot(x = chlorides, data = df)

p9 <- qplot(x = total.sulfur.dioxide, data = df)

p10 <- qplot(x = pH, data = df)

p11 <- qplot(x = alcohol, data = df)

  
grid.arrange(p1, p2, p3, p4, p5, p6, p7, p8, p9, p10, p11, ncol = 3)  

```

#####Here I have categorized each plots

- Right-Skewed: alcohol, citric acid, sulphates, Free sulfur dioxide, Fixed acidity,  Total sulfur, chlorides

- Symetric: density, PH, volatile.acidity, fixed acidity

### Did you create any new variables from existing variables in the dataset?

Yes, I did create new variables to assembled all the plots in one box to faciliate my observations. 

### Of the features you investigated, were there any unusual distributions? \
###Did you perform any operations on the data to tidy, adjust, or change the form \
###of the data? If so, why did you do this?

I used the log10 or squrt by transforming my plots into a normal distribution. I am going to quote from r-statistics.com to explain why I made them normal. "The need for data transformation can depend on the modeling method that you plan to use. For linear and logistic regression, for example, you ideally want to make sure that the relationship between input variables and output variables is approximately linear, that the input variables are approximately normal in distribution, and that the output variable is constant variance (that is, the variance of the output variable is independent of the input variables). You may need to transform some of your input variables to better meet these assumptions."

source: https://www.r-statistics.com/2013/05/log-transformations-for-skewed-and-wide-distributions-from-practical-data-science-with-r/

------------------------------------

# Bivariate Plots Section

I am going to use scatterplots to check the relationship between two variables. 

```{r echo=FALSE, message=FALSE, warning=FALSE, packages part 2}}
library('GGally')
library('scales')
library('memisc')
library("lattice")
```

GGpairs can be useful for exploring the
relationships between several columns of data in a data frame

source: https://stackoverflow.com/questions/45044157/how-do-you-add-jitter-to-a-scatterplot-matrix-in-ggpairs

```{r echo=FALSE, Bivariate_Plots,message=FALSE, warning=FALSE, fig.width=20, fig.height=20}
#I'm going to ggpairs 13 columns 

ggpairs(df, columns = 2:13)

```
-Also, the citric acid do have connection to pH and density. 

-The ones that are little bit closer to citric acid are volatile acidity and fixed acidity. --Meaning, they are probably in relationship. 

First, I need to double check by adding red line or linear regression to see the connection connection between two supportive variables. 

####I am comparing pH and density.

```{r echo=FALSE, message=FALSE, warning=FALSE}

df$quality <- factor(df$quality)

ggplot(data = df, aes(x = pH, y = density, color = quality))+
  geom_jitter()+
  coord_cartesian(ylim = c(0.985, 1.0))+
  scale_color_brewer(type= 'seq')+
  geom_smooth(method = 'lm',color = 'red')+
  theme_dark() +
  labs(x = 'pH', 
       y = 'density(g/cm^3)',
       title= "Alcohol Vs density")

```



```{r echo=FALSE, message=FALSE, warning=FALSE}

df$quality <- factor(df$quality)

ggplot(data = df, aes(x = pH, y = citric.acid, color = quality))+
  geom_jitter()+
  coord_cartesian(ylim = c(0.0, 1.0))+
  scale_color_brewer(type= 'seq')+
  geom_smooth(method = 'lm',color = 'red')+
  theme_dark() +
  labs(x = 'pH', 
       y = 'citric acid',
       title= "ph Vs citric acid")
```

Despite that density looks equally similar to pH; it looks different to citric acid ---comparing to pH and citric acid (check my previous plot). 

```{r echo=FALSE, message=FALSE, warning=FALSE}

df$quality <- factor(df$quality)

ggplot(data = df, aes(x = citric.acid, y = density, color = quality))+
  geom_jitter()+
  coord_cartesian(ylim = c(0.985, 1.02))+
  scale_color_brewer(type= 'seq')+
  geom_smooth(method = 'lm',color = 'red')+
  theme_dark() +
  labs(x = 'citric acid', 
       y = 'density(g/cm^3)',
       title= "Citric Acid Vs Density")
```

Here is the relationship between fixed acidity and ph. 

```{r echo=FALSE, message=FALSE, warning=FALSE}
 
df$quality <- factor(df$quality)

ggplot(data = df, aes(x = fixed.acidity, y = pH, color = quality))+
  geom_jitter()+
  coord_cartesian(ylim = c(0.5, 5))+
  scale_color_brewer(type= 'seq')+
  geom_smooth(method = 'lm',color = 'red')+
  theme_dark() +
  labs(x = 'fixed.acidity', 
       y = 'pH',
       title= "Fixed Acidity Vs. pH")
```

Alright, I am going to compare fixed acidity and citric.acid. They are so connected to each other. 

```{r echo=FALSE, message=FALSE, warning=FALSE}

df$quality <- factor(df$quality)

ggplot(data = df, aes(x = fixed.acidity, y = citric.acid, color = quality))+
  geom_jitter()+
  coord_cartesian(ylim = c(0.0, 1))+
  scale_color_brewer(type= 'seq')+
  geom_smooth(method = 'lm',color = 'red')+
  theme_dark() +
  labs(x = 'Fixed Acidity', 
       y = 'Citric Acid',
       title= "Fixed Acidity Vs. Citric Acid")
```

Next, I am going to plot volatile.acid and fixed.acidity. 

```{r echo=FALSE, message=FALSE, warning=FALSE}
df$quality <- factor(df$quality)

ggplot(data = df, aes(x = fixed.acidity, y = volatile.acidity, color = quality))+
  geom_jitter()+
  coord_cartesian(ylim = c(0.0, 1))+
  scale_color_brewer(type= 'seq')+
  geom_smooth(method = 'lm',color = 'red')+
  theme_dark() +
  labs(x = 'Fixed Acidity', 
       y = 'Volatile Acidity',
       title= "Fixed Acidity Vs. Volatile Acidity")
```

Let's see how it looks like with pH and volatile.acidity. 

```{r echo=FALSE, message=FALSE, warning=FALSE}
df$quality <- factor(df$quality)

ggplot(data = df, aes(x = pH, y = volatile.acidity, color = quality))+
  geom_jitter()+
  coord_cartesian(ylim = c(0.0, 1))+
  scale_color_brewer(type= 'seq')+
  geom_smooth(method = 'lm',color = 'red')+
  theme_dark() +
  labs(x = 'pH', 
       y = 'Volatile Acidity',
       title= "Fixed Acidity Vs. Volatile Acidity")
```

Next, it would volatile.acidity and density:

```{r echo=FALSE, message=FALSE, warning=FALSE}
df$quality <- factor(df$quality)

ggplot(data = df, aes(x = density, y = volatile.acidity, color = quality))+
  geom_jitter()+
  coord_cartesian(ylim = c(0.0, 1))+
  scale_color_brewer(type= 'seq')+
  geom_smooth(method = 'lm',color = 'red')+
  theme_dark() +
  labs(x = 'Density', 
       y = 'Volatile Acidity',
       title= "Density Vs. Volatile Acidity")
```

This is how I categorized visually based on my previous plots.  

#####Positive correlation: (3 pos)
density & citric. acidity, citric & fixed acidity, volatile. acidity & and pH. 

#####Negative correlation: (4 neg)
pH & density, pH & citric acidity, pH & fixed acidity, volatile.acidity & fixed acidity. 

-----------------

Another way to verify if they are negative or positive correlation. I am using a cor.test in programming. 

```{r echo=FALSE, message=FALSE, warning=FALSE}
#negative:
cor.test(df$pH, df$density, method = 'pearson')
cor.test(df$pH, df$citric.acid, method = 'pearson')
cor.test(df$pH, df$fixed.acidity, method = 'pearson')
cor.test(df$fixed.acidity, df$volatile.acidity, method = 'pearson')

#positive:
cor.test(df$pH, df$volatile.acidity, method = 'pearson')
cor.test(df$density, df$citric.acid, method = 'pearson')
cor.test(df$pH, df$volatile.acidity, method = 'pearson')

```

-I am going to use ggcorr as an another method to check the relationshipness between two variables. 

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width= 20, fig.height = 20}

ggcorr(df,
       method= c("all.obs", "spearman"),
       nbreaks = 4, label = TRUE,
       name = "Spearman Correlation Coeff Matrix",
       hjust= 0.8, angle = -70, size = 5)+
  ggtitle("Spearman Correlation coefficient Matrix")

```

I guess this method is easier because you can see that the bright red color is indicating the positive relationship between two variables.These indicate the list of strongest relationship.

1. Free sulfur dioxide & total sulfur dioxide

2. Fixed acidity & Citric Adid

3. density & fixed acidity

# Bivariate Analysis

### Talk about some of the relationships you observed in this part of the \
##investigation. How did the feature(s) of interest vary with other features in \
##the dataset?

source: https://www.emathzone.com/tutorials/basic-statistics/positive-and-negative-correlation.html#ixzz5OmFgYWlq

If a correlation goes to the same direction, is called a positive correlation. If one variable increases, the other also increases. If other variable decreases, the other decreases as well. 

If the correlation goes to the oppposite direction, it is called negative correlation. If one variables increases, other should decrease. 

After observing the table, I see two similarity between density and pH. They both have normal looking plot and symetrical.


### Did you observe any interesting relationships between the other features \
###(not the main feature(s) of interest)?

Yes. I did. I have compared the ph, density, citric.accidity, and others variables that might seem to be correlated to each other. 


### What was the strongest relationship you found?

The List of the strongest relationship:

1. Free sulfur dioxide & total sulfur dioxide

2. Fixed acidity & Citric Adid

3. density & fixed acidity
##### Checking out the boxplots

--> Quality of Wine and other variables in boxplots

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width= 20, fig.height = 20}
Q_A<- ggplot(data = df, aes(x= factor(quality), y = alcohol))+
  geom_jitter(alpha = 1/10)+
  geom_boxplot(alpha = 1/10, color = 'blue')+
  stat_summary(fun.y = 'mean', geom = 'point', color = 'red')+
  labs(x = 'Quality (score between 3 and 9)',
       y = 'Alcohol (% by volume)',
       title = 'Boxplot of alcohol across qualities')

Q_S <- ggplot(data = df, aes(x= factor(quality), y = sulphates))+
  geom_jitter(alpha = 1/10)+
  geom_boxplot(alpha = 1/10, color = 'blue')+
  stat_summary(fun.y = 'mean', geom = 'point', color = 'red')+
  labs(x = 'Quality (score between 3 and 9)',
       y = 'sulphates (potassium sulphate - g / dm3)',
       title = 'Boxplot of sulphates across qualities')

Q_C <- ggplot(data = df, aes(x= factor(quality), y = citric.acid))+
  geom_jitter(alpha = 1/10)+
  geom_boxplot(alpha = 1/10, color = 'blue')+
  stat_summary(fun.y = 'mean', geom = 'point', color = 'red')+
  labs(x = 'Quality (score between 3 and 9)',
       y = 'citric acid (g / dm^3)',
       title = 'Boxplot of Citric Acid across qualities')

Q_FA <- ggplot(data = df, aes(x= factor(quality), y = fixed.acidity))+
  geom_jitter(alpha = 1/10)+
  geom_boxplot(alpha = 1/10, color = 'blue')+
  stat_summary(fun.y = 'mean', geom = 'point', color = 'red')+
  labs(x = 'Quality (score between 3 and 9)',
       y = 'fixed acidity (tartaric acid - g / dm^3)',
       title = 'Boxplot of Fixed Acidity across qualities')

Q_VA <- ggplot(data = df, aes(x= factor(quality), y = volatile.acidity))+
  geom_jitter(alpha = 1/10)+
  geom_boxplot(alpha = 1/10, color = 'blue')+
  stat_summary(fun.y = 'mean', geom = 'point', color = 'red')+
  labs(x = 'Quality (score between 3 and 9)',
       y = 'volatile acidity (acetic acid - g / dm^3)',
       title = 'Boxplot of Volitle Acidity across qualities')

Q_P <- ggplot(data = df, aes(x= factor(quality), y = pH))+
  geom_jitter(alpha = 1/10)+
  geom_boxplot(alpha = 1/10, color = 'blue')+
  stat_summary(fun.y = 'mean', geom = 'point', color = 'red')+
  labs(x = 'Quality (score between 3 and 9)',
       y = 'pH',
       title = 'Boxplot of pH across qualities')

Q_D <- ggplot(data = df, aes(x= factor(quality), y = density))+
  geom_jitter(alpha = 1/10)+
  geom_boxplot(alpha = 1/10, color = 'blue')+
  stat_summary(fun.y = 'mean', geom = 'point', color = 'red')+
  labs(x = 'Quality (score between 3 and 9)',
       y = 'density (g / cm^3)',
       title = 'Boxplot of density across qualities')

Q_TSD <- ggplot(data = df, aes(x= factor(quality), y = total.sulfur.dioxide))+
  geom_jitter(alpha = 1/10)+
  geom_boxplot(alpha = 1/10, color = 'blue')+
  stat_summary(fun.y = 'mean', geom = 'point', color = 'red')+
  labs(x = 'Quality (score between 3 and 9)',
       y = 'total sulfur dioxide (mg / dm^3)',
       title = 'Boxplot of total sulfur dioxide across qualities')

Q_RS <- ggplot(data = df, aes(x= factor(quality), y = df$residual.sugar))+
  geom_jitter(alpha = 1/10)+
  geom_boxplot(alpha = 1/10, color = 'blue')+
  stat_summary(fun.y = 'mean', geom = 'point', color = 'red')+
  labs(x = 'Quality (score between 3 and 9)',
       y = 'residual sugar (g / dm^3)',
       title = 'Boxplot of residual sugar across qualities')

grid.arrange(Q_A,Q_S,Q_C,Q_FA,Q_VA,Q_P,Q_D,Q_TSD,Q_RS,ncol = 3)

```

--------------------------------
# Multivariate Plots Section

> **Tip**: Now it's time to put everything together. Based on what you found in
the bivariate plots section, create a few multivariate plots to investigate
more complex interactions between variables. Make sure that the plots that you
create here are justified by the plots you explored in the previous section. If
you plan on creating any mathematical models, this is the section where you
will do that.

```{r echo=FALSE, Multivariate_Plots}

```

# Multivariate Analysis

### Talk about some of the relationships you observed in this part of the \
investigation. Were there features that strengthened each other in terms of \
looking at your feature(s) of interest?

### Were there any interesting or surprising interactions between features?

### OPTIONAL: Did you create any models with your dataset? Discuss the \
strengths and limitations of your model.

------

# Final Plots and Summary

> **Tip**: You've done a lot of exploration and have built up an understanding
of the structure of and relationships between the variables in your dataset.
Here, you will select three plots from all of your previous exploration to
present here as a summary of some of your most interesting findings. Make sure
that you have refined your selected plots for good titling, axis labels (with
units), and good aesthetic choices (e.g. color, transparency). After each plot,
make sure you justify why you chose each plot by describing what it shows.

### Plot One
```{r echo=FALSE, Plot_One}

```

### Description One


### Plot Two
```{r echo=FALSE, Plot_Two}

```

### Description Two


### Plot Three
```{r echo=FALSE, Plot_Three}

```

### Description Three

------

# Reflection

> **Tip**: Here's the final step! Reflect on the exploration you performed and
the insights you found. What were some of the struggles that you went through?
What went well? What was surprising? Make sure you include an insight into
future work that could be done with the dataset.

> **Tip**: Don't forget to remove this, and the other **Tip** sections before
saving your final work and knitting the final report!